### 2014-03-14 src/analysis.Rnw
.

o.stats.sel.op <- o.stats.sel.op[,c(1,7,2,3,4,5,6)]
r.stats.sel.op <- r.stats.sel.op[,c(1,7,2,3,4,5,6)]

@@

o.stats.sel.opsel <- o.stats.sel.opsel[,c(1,7,2,3,4,5,6)]
r.stats.sel.opsel <- r.stats.sel.opsel[,c(1,7,2,3,4,5,6)]

>>>>

o.stats.sel.op <- o.stats.sel.op[,c(0,6,1,2,3,4,5)]
r.stats.sel.op <- r.stats.sel.op[,c(0,6,1,2,3,4,5)]

@@

o.stats.sel.opsel <- o.stats.sel.opsel[,c(0,6,1,2,3,4,5)]
r.stats.sel.opsel <- r.stats.sel.opsel[,c(0,6,1,2,3,4,5)]
